---
title: "SOC_Incentive_Carinata"
Author: Kazi Masel Ullah
date: "2023-03-15"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r set Library, include=FALSE}
library(tidyverse)
library(ggplot2)
library(gtable)
library(gridExtra)
library(grid)
setwd("C:/ABMUpscale/Result")
```

## Data for BaU Scenario 
```{r BR40, echo=FALSE}
dfBaU <- read_csv("BR40.csv", col_names = TRUE, skip = 6)
head(dfBaU)
dfBaU$Run <- dfBaU$`[run number]` 
dfBaU$Year = 2017 + dfBaU$`[step]`*3
dfBaU$DiffusType <- dfBaU$`TraditionalDiffusion?`
dfBaU$WillingType <- dfBaU$`LowWillingness?`
dfBaU$Price <- dfBaU$CarinataPrice
dfBaU$SOCInstv <- dfBaU$SOCIncentive
dfBaU$AdoptNo <- dfBaU$`count turtles with [a? = TRUE and color = green]`*5 +
                      dfBaU$`count turtles with [a? = TRUE and color = yellow]`*5 +
                      dfBaU$`count turtles with [a? = TRUE and color = white]`*5
dfBaU$Land <- dfBaU$TotLandAllocate * 5 / 1000  ## '000 acre unit
dfBaU <- dfBaU[, c(which(colnames(dfBaU) =="Run"): ncol(dfBaU))] 
head(dfBaU)

```

## Data for No-Till Scenario 
```{r NTR40}
dfNT <- read_csv("NTR40.csv", col_names = TRUE, skip = 6)
head(dfNT)
dfNT$Run <- dfNT$`[run number]` 
dfNT$Year = 2017 + dfNT$`[step]`*3
dfNT$DiffusType <- dfNT$`TraditionalDiffusion?`
dfNT$WillingType <- dfNT$`LowWillingness?`
dfNT$Price <- dfNT$CarinataPrice
dfNT$SOCInstv <- dfNT$SOCIncentive
dfNT$AdoptNo <- dfNT$`count turtles with [a? = TRUE and color = green]`*5 +
                      dfNT$`count turtles with [a? = TRUE and color = yellow]`*5 +
                      dfNT$`count turtles with [a? = TRUE and color = white]`*5
dfNT$Land <- dfNT$TotLandAllocate * 5 / 1000 ## '000 acre unit
dfNT <- dfNT[, c(which(colnames(dfNT) =="Run"): ncol(dfNT))] 
head(dfNT)

```

## Figure 6

The total number of farmers who adopted carinata over the years for two farming scenarios at five levels of incentives for SOC sequestration and at the three price levels. 

#### Peice $5, Expansion Diffusion, Low Initial Willingness Scenario 

```{r Plot_a, echo=FALSE}
df <- dfBaU %>% filter(Price == 5 & DiffusType == FALSE & WillingType == TRUE)
df <- aggregate(AdoptNo~SOCInstv+Year, data=df, FUN="mean")
#view(df)
df$SOCInstv <- paste("$", df$SOCInstv, sep = "")
df$SOCInstv <- factor(df$SOCInstv, levels = c(paste("$", c(0, 50, 100, 150, 200), sep = "")), labels = c(paste("$", c(0, 50, 100, 150, 200), sep = "")))

Plot_a <- ggplot(data = df, mapping = aes(x = Year, y = AdoptNo,
                                               group = SOCInstv, colour = SOCInstv, shape=SOCInstv)) +
  geom_line(size=0.75) +
  geom_point(size=2) +
  #scale_shape_discrete("SOC Incetive $/Mg CO2") +
  #scale_colour_discrete("SOC Incetive $/Mg CO2") +
  scale_linetype_discrete("SOC Incetive $/Mg CO2")+
  #scale_fill_manual("SOC Incetive $/Mg CO2") +
  xlab("Time Steps") + ylab("No. of Adopters") +
  scale_y_continuous(limits = c(0, 20000), breaks = seq(0, 20000, by = 4000)) +
  scale_x_continuous(breaks=c(2017, 2020, 2023, 2026, 2029, 2032, 2035, 2038, 2041, 2044, 2047, 2050)) +
  theme_bw() +
  theme_classic()+
  labs(subtitle =  "Price at $5/bu") +
  # theme(axis.text.x = element_text(colour = "grey20", size = 14, angle = 90, hjust = 0.5, vjust = 0.5),
  #       axis.text.y = element_text(colour = "grey20", size = 14),
  #       strip.text = element_text(face = "italic"),
  #       text = element_text(size = 16),
  #       plot.subtitle=element_text(size=20)) +  
  theme(legend.position="none",
        axis.title.x = element_text(vjust=-1.5)) 

Plot_a
```

#### Peice $5.5, Expansion Diffusion, Low Initial Willingness Scenario 
```{r Plot_b, echo=FALSE}
df <- dfBaU %>% filter(Price == 5.5 & DiffusType == FALSE & WillingType == TRUE)
df <- aggregate(AdoptNo~SOCInstv+Year, data=df, FUN="mean")
#view(df)
df$SOCInstv <- paste("$", df$SOCInstv, sep = "")
df$SOCInstv <- factor(df$SOCInstv, levels = c(paste("$", c(0, 50, 100, 150, 200), sep = "")), labels = c(paste("$", c(0, 50, 100, 150, 200), sep = "")))

Plot_b <- ggplot(data = df, mapping = aes(x = Year, y = AdoptNo,
                                               group = SOCInstv, colour = SOCInstv, shape=SOCInstv)) +
  geom_line(size=0.75) +
  geom_point(size=2) +
  #scale_shape_discrete("SOC Incetive $/Mg CO2") +
  #scale_colour_discrete("SOC Incetive $/Mg CO2") +
  scale_linetype_discrete("SOC Incetive $/Mg CO2")+
  #scale_fill_manual("SOC Incetive $/Mg CO2") +
  xlab("Time Steps") + ylab("No. of Adopters") +
  scale_y_continuous(limits = c(0, 20000), breaks = seq(0, 20000, by = 4000)) +
  scale_x_continuous(breaks=c(2017, 2020, 2023, 2026, 2029, 2032, 2035, 2038, 2041, 2044, 2047, 2050)) +
  theme_bw() +
  theme_classic()+
  labs(subtitle =  "Price at $5.5/bu") +
  # theme(axis.text.x = element_text(colour = "grey20", size = 14, angle = 90, hjust = 0.5, vjust = 0.5),
  #       axis.text.y = element_text(colour = "grey20", size = 14),
  #       strip.text = element_text(face = "italic"),
  #       text = element_text(size = 16),
  #       plot.subtitle=element_text(size=20)) +  
  theme(legend.position="none",
        axis.title.x = element_text(vjust=-1.5)) 

Plot_b
```

#### Peice $6, Expansion Diffusion, Low Initial Willingness Scenario 
```{r Plot_c, echo=FALSE}
df <- dfBaU %>% filter(Price == 6 & DiffusType == FALSE & WillingType == TRUE)
df <- aggregate(AdoptNo~SOCInstv+Year, data=df, FUN="mean")
#view(df)
df$SOCInstv <- paste("$", df$SOCInstv, sep = "")
df$SOCInstv <- factor(df$SOCInstv, levels = c(paste("$", c(0, 50, 100, 150, 200), sep = "")), labels = c(paste("$", c(0, 50, 100, 150, 200), sep = "")))

Plot_c <- ggplot(data = df, mapping = aes(x = Year, y = AdoptNo,
                                               group = SOCInstv, colour = SOCInstv, shape=SOCInstv)) +
  geom_line(size=0.75) +
  geom_point(size=2) +
  #scale_shape_discrete("SOC Incetive $/Mg CO2") +
  #scale_colour_discrete("SOC Incetive $/Mg CO2") +
  scale_linetype_discrete("SOC Incetive $/Mg CO2")+
  #scale_fill_manual("SOC Incetive $/Mg CO2") +
  xlab("Time Steps") + ylab("No. of Adopters") +
  scale_y_continuous(limits = c(0, 20000), breaks = seq(0, 20000, by = 4000)) +
  scale_x_continuous(breaks=c(2017, 2020, 2023, 2026, 2029, 2032, 2035, 2038, 2041, 2044, 2047, 2050)) +
  theme_bw() +
  theme_classic()+
  labs(subtitle =  "Price at $6/bu") +
  # theme(axis.text.x = element_text(colour = "grey20", size = 14, angle = 90, hjust = 0.5, vjust = 0.5),
  #       axis.text.y = element_text(colour = "grey20", size = 14),
  #       strip.text = element_text(face = "italic"),
  #       text = element_text(size = 16),
  #       plot.subtitle=element_text(size=20)) +  
  theme(legend.position="none",
        axis.title.x = element_text(vjust=-1.5)) 

Plot_c
```

#### Peice $5, Expansion Diffusion, Low Initial Willingness Scenario 
```{r Plot d, echo=FALSE}
df <- dfNT %>% filter(Price == 5 & DiffusType == FALSE & WillingType == TRUE)
df <- aggregate(AdoptNo~SOCInstv+Year, data=df, FUN="mean")
#view(df)
df$SOCInstv <- paste("$", df$SOCInstv, sep = "")
df$SOCInstv <- factor(df$SOCInstv, levels = c(paste("$", c(0, 50, 100, 150, 200), sep = "")), labels = c(paste("$", c(0, 50, 100, 150, 200), sep = "")))

Plot_d <- ggplot(data = df, mapping = aes(x = Year, y = AdoptNo,
                                               group = SOCInstv, colour = SOCInstv, shape=SOCInstv)) +
  geom_line(size=0.75) +
  geom_point(size=2) +
  #scale_shape_discrete("SOC Incetive $/Mg CO2") +
  #scale_colour_discrete("SOC Incetive $/Mg CO2") +
  scale_linetype_discrete("SOC Incetive $/Mg CO2")+
  #scale_fill_manual("SOC Incetive $/Mg CO2") +
  xlab("Time Steps") + ylab("No. of Adopters") +
  scale_y_continuous(limits = c(0, 20000), breaks = seq(0, 20000, by = 4000)) +
  scale_x_continuous(breaks=c(2017, 2020, 2023, 2026, 2029, 2032, 2035, 2038, 2041, 2044, 2047, 2050)) +
  theme_bw() +
  theme_classic()+
  labs(subtitle =  "Price at $5/bu") +
  # theme(axis.text.x = element_text(colour = "grey20", size = 14, angle = 90, hjust = 0.5, vjust = 0.5),
  #       axis.text.y = element_text(colour = "grey20", size = 14),
  #       strip.text = element_text(face = "italic"),
  #       text = element_text(size = 16),
  #       plot.subtitle=element_text(size=20)) +  
  theme(legend.position="none",
        axis.title.x = element_text(vjust=-1.5)) 

Plot_d
```

#### Peice $5.5, Expansion Diffusion, Low Initial Willingness Scenario 
```{r Plot_e, echo=FALSE}
df <- dfNT %>% filter(Price == 5.5 & DiffusType == FALSE & WillingType == TRUE)
df <- aggregate(AdoptNo~SOCInstv+Year, data=df, FUN="mean")
#view(df)
df$SOCInstv <- paste("$", df$SOCInstv, sep = "")
df$SOCInstv <- factor(df$SOCInstv, levels = c(paste("$", c(0, 50, 100, 150, 200), sep = "")), labels = c(paste("$", c(0, 50, 100, 150, 200), sep = "")))

Plot_e <- ggplot(data = df, mapping = aes(x = Year, y = AdoptNo,
                                               group = SOCInstv, colour = SOCInstv, shape=SOCInstv)) +
  geom_line(size=0.75) +
  geom_point(size=2) +
  #scale_shape_discrete("SOC Incetive $/Mg CO2") +
  #scale_colour_discrete("SOC Incetive $/Mg CO2") +
  scale_linetype_discrete("SOC Incetive $/Mg CO2")+
  #scale_fill_manual("SOC Incetive $/Mg CO2") +
  xlab("Time Steps") + ylab("No. of Adopters") +
  scale_y_continuous(limits = c(0, 20000), breaks = seq(0, 20000, by = 4000)) +
  scale_x_continuous(breaks=c(2017, 2020, 2023, 2026, 2029, 2032, 2035, 2038, 2041, 2044, 2047, 2050)) +
  theme_bw() +
  theme_classic()+
  labs(subtitle =  "Price at $5.5/bu") +
  # theme(axis.text.x = element_text(colour = "grey20", size = 14, angle = 90, hjust = 0.5, vjust = 0.5),
  #       axis.text.y = element_text(colour = "grey20", size = 14),
  #       strip.text = element_text(face = "italic"),
  #       text = element_text(size = 16),
  #       plot.subtitle=element_text(size=20)) +  
  theme(legend.position="none",
        axis.title.x = element_text(vjust=-1.5)) 

Plot_e
```

#### Peice $6, Expansion Diffusion, Low Initial Willingness Scenario 
```{r Plot_f, echo=FALSE}
df <- dfNT %>% filter(Price == 6 & DiffusType == FALSE & WillingType == TRUE)
df <- aggregate(AdoptNo~SOCInstv+Year, data=df, FUN="mean")
#view(df)
df$SOCInstv <- paste("$", df$SOCInstv, sep = "")
df$SOCInstv <- factor(df$SOCInstv, levels = c(paste("$", c(0, 50, 100, 150, 200), sep = "")), labels = c(paste("$", c(0, 50, 100, 150, 200), sep = "")))

Plot_f <- ggplot(data = df, mapping = aes(x = Year, y = AdoptNo,
                                               group = SOCInstv, colour = SOCInstv, shape=SOCInstv)) +
  geom_line(size=0.75) +
  geom_point(size=2) +
  #scale_shape_discrete("SOC Incetive $/Mg CO2") +
  #scale_colour_discrete("SOC Incetive $/Mg CO2") +
  scale_linetype_discrete("SOC Incetive $/Mg CO2")+
  #scale_fill_manual("SOC Incetive $/Mg CO2") +
  xlab("Time Steps") + ylab("No. of Adopters") +
  scale_y_continuous(limits = c(0, 20000), breaks = seq(0, 20000, by = 4000)) +
  scale_x_continuous(breaks=c(2017, 2020, 2023, 2026, 2029, 2032, 2035, 2038, 2041, 2044, 2047, 2050)) +
  theme_bw() +
  theme_classic()+
  labs(subtitle =  "Price at $6/bu") +
  # theme(axis.text.x = element_text(colour = "grey20", size = 14, angle = 90, hjust = 0.5, vjust = 0.5),
  #       axis.text.y = element_text(colour = "grey20", size = 14),
  #       strip.text = element_text(face = "italic"),
  #       text = element_text(size = 16),
  #       plot.subtitle=element_text(size=20)) +  
  theme(legend.position="bottom",
        axis.title.x = element_text(vjust=-1.5)) 

Plot_f
Legend = gtable_filter(ggplot_gtable(ggplot_build(Plot_f)), "guide-box")
```

##### Maring all the plots 
```{r merge, echo=FALSE, fig.width=10, fig.height=8}


grid.arrange(arrangeGrob(Plot_a, Plot_b, Plot_c, top="BaU Farming", ncol=1), 
              arrangeGrob(Plot_d, Plot_e, Plot_f + theme(legend.position="none"), top="No-Till Farming", ncol = 1), 
             bottom = Legend,
              ncol=2)

```


## Figure 7

The total land allocated by the adopters over the years for two farming scenarios at five levels of incentives for SOC sequestration and at the three price levels. 

#### Peice $5, Expansion Diffusion, Low Initial Willingness Scenario 

```{r Plot_a, echo=FALSE}
df <- dfBaU %>% filter(Price == 5 & DiffusType == FALSE & WillingType == TRUE)
df <- aggregate(Land~SOCInstv+Year, data=df, FUN="mean")
#view(df)
df$SOCInstv <- paste("$", df$SOCInstv, sep = "")
df$SOCInstv <- factor(df$SOCInstv, levels = c(paste("$", c(0, 50, 100, 150, 200), sep = "")), labels = c(paste("$", c(0, 50, 100, 150, 200), sep = "")))

Plot_a <- ggplot(data = df, mapping = aes(x = Year, y = Land,
                                               group = SOCInstv, colour = SOCInstv, shape=SOCInstv)) +
  geom_line(size=0.75) +
  geom_point(size=2) +
  #scale_shape_discrete("SOC Incetive $/Mg CO2") +
  #scale_colour_discrete("SOC Incetive $/Mg CO2") +
  scale_linetype_discrete("SOC Incetive $/Mg CO2")+
  #scale_fill_manual("SOC Incetive $/Mg CO2") +
  xlab("Time Steps") + ylab("Land ('000 acre)") +
  scale_y_continuous(limits = c(0, 2000), breaks = seq(0, 2000, by = 400)) +
  scale_x_continuous(breaks=c(2017, 2020, 2023, 2026, 2029, 2032, 2035, 2038, 2041, 2044, 2047, 2050)) +
  theme_bw() +
  theme_classic()+
  labs(subtitle =  "Price at $5/bu") +
  # theme(axis.text.x = element_text(colour = "grey20", size = 14, angle = 90, hjust = 0.5, vjust = 0.5),
  #       axis.text.y = element_text(colour = "grey20", size = 14),
  #       strip.text = element_text(face = "italic"),
  #       text = element_text(size = 16),
  #       plot.subtitle=element_text(size=20)) +  
  theme(legend.position="none",
        axis.title.x = element_text(vjust=-1.5)) 

Plot_a
```

#### Peice $5.5, Expansion Diffusion, Low Initial Willingness Scenario 
```{r Plot_b, echo=FALSE}
df <- dfBaU %>% filter(Price == 5.5 & DiffusType == FALSE & WillingType == TRUE)
df <- aggregate(Land~SOCInstv+Year, data=df, FUN="mean")
#view(df)
df$SOCInstv <- paste("$", df$SOCInstv, sep = "")
df$SOCInstv <- factor(df$SOCInstv, levels = c(paste("$", c(0, 50, 100, 150, 200), sep = "")), labels = c(paste("$", c(0, 50, 100, 150, 200), sep = "")))

Plot_b <- ggplot(data = df, mapping = aes(x = Year, y = Land,
                                               group = SOCInstv, colour = SOCInstv, shape=SOCInstv)) +
  geom_line(size=0.75) +
  geom_point(size=2) +
  #scale_shape_discrete("SOC Incetive $/Mg CO2") +
  #scale_colour_discrete("SOC Incetive $/Mg CO2") +
  scale_linetype_discrete("SOC Incetive $/Mg CO2")+
  #scale_fill_manual("SOC Incetive $/Mg CO2") +
  xlab("Time Steps") + ylab("Land ('000 acre)") +
  scale_y_continuous(limits = c(0, 2000), breaks = seq(0, 2000, by = 400)) +
  scale_x_continuous(breaks=c(2017, 2020, 2023, 2026, 2029, 2032, 2035, 2038, 2041, 2044, 2047, 2050)) +
  theme_bw() +
  theme_classic()+
  labs(subtitle =  "Price at $5.5/bu") +
  # theme(axis.text.x = element_text(colour = "grey20", size = 14, angle = 90, hjust = 0.5, vjust = 0.5),
  #       axis.text.y = element_text(colour = "grey20", size = 14),
  #       strip.text = element_text(face = "italic"),
  #       text = element_text(size = 16),
  #       plot.subtitle=element_text(size=20)) +  
  theme(legend.position="none",
        axis.title.x = element_text(vjust=-1.5)) 

Plot_b
```

#### Peice $6, Expansion Diffusion, Low Initial Willingness Scenario 
```{r Plot_c, echo=FALSE}
df <- dfBaU %>% filter(Price == 6 & DiffusType == FALSE & WillingType == TRUE)
df <- aggregate(Land~SOCInstv+Year, data=df, FUN="mean")
#view(df)
df$SOCInstv <- paste("$", df$SOCInstv, sep = "")
df$SOCInstv <- factor(df$SOCInstv, levels = c(paste("$", c(0, 50, 100, 150, 200), sep = "")), labels = c(paste("$", c(0, 50, 100, 150, 200), sep = "")))

Plot_c <- ggplot(data = df, mapping = aes(x = Year, y = Land,
                                               group = SOCInstv, colour = SOCInstv, shape=SOCInstv)) +
  geom_line(size=0.75) +
  geom_point(size=2) +
  #scale_shape_discrete("SOC Incetive $/Mg CO2") +
  #scale_colour_discrete("SOC Incetive $/Mg CO2") +
  scale_linetype_discrete("SOC Incetive $/Mg CO2")+
  #scale_fill_manual("SOC Incetive $/Mg CO2") +
  xlab("Time Steps") + ylab("Land ('000 acre)") +
  scale_y_continuous(limits = c(0, 2000), breaks = seq(0, 2000, by = 400)) +
  scale_x_continuous(breaks=c(2017, 2020, 2023, 2026, 2029, 2032, 2035, 2038, 2041, 2044, 2047, 2050)) +
  theme_bw() +
  theme_classic()+
  labs(subtitle =  "Price at $6/bu") +
  # theme(axis.text.x = element_text(colour = "grey20", size = 14, angle = 90, hjust = 0.5, vjust = 0.5),
  #       axis.text.y = element_text(colour = "grey20", size = 14),
  #       strip.text = element_text(face = "italic"),
  #       text = element_text(size = 16),
  #       plot.subtitle=element_text(size=20)) +  
  theme(legend.position="none",
        axis.title.x = element_text(vjust=-1.5)) 

Plot_c
```

#### Peice $5, Expansion Diffusion, Low Initial Willingness Scenario 
```{r Plot d, echo=FALSE}
df <- dfNT %>% filter(Price == 5 & DiffusType == FALSE & WillingType == TRUE)
df <- aggregate(Land~SOCInstv+Year, data=df, FUN="mean")
#view(df)
df$SOCInstv <- paste("$", df$SOCInstv, sep = "")
df$SOCInstv <- factor(df$SOCInstv, levels = c(paste("$", c(0, 50, 100, 150, 200), sep = "")), labels = c(paste("$", c(0, 50, 100, 150, 200), sep = "")))

Plot_d <- ggplot(data = df, mapping = aes(x = Year, y = Land,
                                               group = SOCInstv, colour = SOCInstv, shape=SOCInstv)) +
  geom_line(size=0.75) +
  geom_point(size=2) +
  #scale_shape_discrete("SOC Incetive $/Mg CO2") +
  #scale_colour_discrete("SOC Incetive $/Mg CO2") +
  scale_linetype_discrete("SOC Incetive $/Mg CO2")+
  #scale_fill_manual("SOC Incetive $/Mg CO2") +
  xlab("Time Steps") + ylab("Land ('000 acre)") +
  scale_y_continuous(limits = c(0, 2000), breaks = seq(0, 2000, by = 400)) +
  scale_x_continuous(breaks=c(2017, 2020, 2023, 2026, 2029, 2032, 2035, 2038, 2041, 2044, 2047, 2050)) +
  theme_bw() +
  theme_classic()+
  labs(subtitle =  "Price at $5/bu") +
  # theme(axis.text.x = element_text(colour = "grey20", size = 14, angle = 90, hjust = 0.5, vjust = 0.5),
  #       axis.text.y = element_text(colour = "grey20", size = 14),
  #       strip.text = element_text(face = "italic"),
  #       text = element_text(size = 16),
  #       plot.subtitle=element_text(size=20)) +  
  theme(legend.position="none",
        axis.title.x = element_text(vjust=-1.5)) 

Plot_d
```

#### Peice $5.5, Expansion Diffusion, Low Initial Willingness Scenario 
```{r Plot_e, echo=FALSE}
df <- dfNT %>% filter(Price == 5.5 & DiffusType == FALSE & WillingType == TRUE)
df <- aggregate(Land~SOCInstv+Year, data=df, FUN="mean")
#view(df)
df$SOCInstv <- paste("$", df$SOCInstv, sep = "")
df$SOCInstv <- factor(df$SOCInstv, levels = c(paste("$", c(0, 50, 100, 150, 200), sep = "")), labels = c(paste("$", c(0, 50, 100, 150, 200), sep = "")))

Plot_e <- ggplot(data = df, mapping = aes(x = Year, y = Land,
                                               group = SOCInstv, colour = SOCInstv, shape=SOCInstv)) +
  geom_line(size=0.75) +
  geom_point(size=2) +
  #scale_shape_discrete("SOC Incetive $/Mg CO2") +
  #scale_colour_discrete("SOC Incetive $/Mg CO2") +
  scale_linetype_discrete("SOC Incetive $/Mg CO2")+
  #scale_fill_manual("SOC Incetive $/Mg CO2") +
  xlab("Time Steps") + ylab("Land ('000 acre)") +
  scale_y_continuous(limits = c(0, 2000), breaks = seq(0, 2000, by = 400)) +
  scale_x_continuous(breaks=c(2017, 2020, 2023, 2026, 2029, 2032, 2035, 2038, 2041, 2044, 2047, 2050)) +
  theme_bw() +
  theme_classic()+
  labs(subtitle =  "Price at $5.5/bu") +
  # theme(axis.text.x = element_text(colour = "grey20", size = 14, angle = 90, hjust = 0.5, vjust = 0.5),
  #       axis.text.y = element_text(colour = "grey20", size = 14),
  #       strip.text = element_text(face = "italic"),
  #       text = element_text(size = 16),
  #       plot.subtitle=element_text(size=20)) +  
  theme(legend.position="none",
        axis.title.x = element_text(vjust=-1.5)) 

Plot_e
```

#### Peice $6, Expansion Diffusion, Low Initial Willingness Scenario 
```{r Plot_f, echo=FALSE}
df <- dfNT %>% filter(Price == 6 & DiffusType == FALSE & WillingType == TRUE)
df <- aggregate(Land~SOCInstv+Year, data=df, FUN="mean")
#view(df)
df$SOCInstv <- paste("$", df$SOCInstv, sep = "")
df$SOCInstv <- factor(df$SOCInstv, levels = c(paste("$", c(0, 50, 100, 150, 200), sep = "")), labels = c(paste("$", c(0, 50, 100, 150, 200), sep = "")))

Plot_f <- ggplot(data = df, mapping = aes(x = Year, y = Land,
                                               group = SOCInstv, colour = SOCInstv, shape=SOCInstv)) +
  geom_line(size=0.75) +
  geom_point(size=2) +
  #scale_shape_discrete("SOC Incetive $/Mg CO2") +
  #scale_colour_discrete("SOC Incetive $/Mg CO2") +
  scale_linetype_discrete("SOC Incetive $/Mg CO2")+
  #scale_fill_manual("SOC Incetive $/Mg CO2") +
  xlab("Time Steps") + ylab("Land ('000 acre)") +
  scale_y_continuous(limits = c(0, 2000), breaks = seq(0, 2000, by = 400)) +
  scale_x_continuous(breaks=c(2017, 2020, 2023, 2026, 2029, 2032, 2035, 2038, 2041, 2044, 2047, 2050)) +
  theme_bw() +
  theme_classic()+
  labs(subtitle =  "Price at $6/bu") +
  # theme(axis.text.x = element_text(colour = "grey20", size = 14, angle = 90, hjust = 0.5, vjust = 0.5),
  #       axis.text.y = element_text(colour = "grey20", size = 14),
  #       strip.text = element_text(face = "italic"),
  #       text = element_text(size = 16),
  #       plot.subtitle=element_text(size=20)) +  
  theme(legend.position="bottom",
        axis.title.x = element_text(vjust=-1.5)) 

Plot_f
Legend = gtable_filter(ggplot_gtable(ggplot_build(Plot_f)), "guide-box")
```

##### Maring all the plots 
```{r merge, echo=FALSE, fig.width=10, fig.height=8}


grid.arrange(arrangeGrob(Plot_a, Plot_b, Plot_c, top="BaU Farming", ncol=1), 
              arrangeGrob(Plot_d, Plot_e, Plot_f + theme(legend.position="none"), top="No-Till Farming", ncol = 1), 
             bottom = Legend,
              ncol=2)

```

## Figure 8 & 9

The total land allocated by the adopters over the years for three scenarios and their associated total SOC sequestrations. Scenario 1 (S1) = base farming, price $5.5, SOC incentive $100; Scenario 2 (S2) = base farming, price $6, SOC incentive $0; Scenario 3 (S3) = No-till farming, price $5.5, SOC incentive $100.  

```{r data for scenarios}
df <- dfBaU %>% filter(Price == 5.5 & SOCInstv == 100 & DiffusType == FALSE & WillingType == TRUE)
df1 <- aggregate(Land~Year, data=df, FUN="mean")
df1$SOC <- df1$Land * 0.12  # average SOC changes in '000 MgCO2e/acre in GA 
df1$Scenario <- "S1"
df1std <- aggregate(Land~Year, data=df, FUN="sd")
df1$SD <- df1std$Land

df <- dfBaU %>% filter(Price == 6 & SOCInstv == 0 & DiffusType == FALSE & WillingType == TRUE)
df2 <- aggregate(Land~Year, data=df, FUN="mean")
df2$SOC <- df2$Land * 0.12  # average SOC changes in GA/acre
df2$Scenario <- "S2"
df2std <- aggregate(Land~Year, data=df, FUN="sd")
df2$SD <- df2std$Land


df <- dfNT %>% filter(Price == 5.5 & SOCInstv == 100 & DiffusType == FALSE & WillingType == TRUE)
df3 <- aggregate(Land~Year, data=df, FUN="mean")
df3$SOC <- df3$Land * 0.42  # average SOC changes in GA/acre
df3$Scenario <- "S3"
df3std <- aggregate(Land~Year, data=df, FUN="sd")
df3$SD <- df3std$Land

Df <- rbind(df1,df2,df3)
#view(Df)
```

### Figure 8: Total land allocation in three scenarios 

```{r Plot_f, echo=FALSE}
Plot_final1 <- ggplot(data = Df, mapping = aes(x = Year, y = Land,
                                          group = Scenario, colour = Scenario)) +
  geom_line(size=1) +
  geom_point(size=3) +
  #scale_shape_discrete("Scenarios") +
  scale_colour_discrete("Scenarios") +
  scale_linetype_discrete("Scenarios")+
  #scale_fill_manual("SOC Incetive $/Mg CO2") + #
  xlab("Time steps") +  ylab("Land ('000 acre) ") +
  scale_y_continuous(limits = c(0, 2000), breaks = seq(0, 2000, by = 400)) +
  scale_x_continuous(breaks=c(2017, 2020, 2023, 2026, 2029, 2032, 2035, 2038, 2041, 2044, 2047, 2050)) +
  theme_bw() +
  theme_classic()+
  labs(subtitle =  "Total land allocation in three scenarios") +
  # theme(axis.text.x = element_text(colour = "grey20", size = 14, angle = 90, hjust = 0.5, vjust = 0.5),
  #       axis.text.y = element_text(colour = "grey20", size = 14),
  #       strip.text = element_text(face = "italic"),
  #       text = element_text(size = 16),
  #       plot.subtitle=element_text(size=20)) +  
  theme(legend.position="bottom",
        axis.title.x = element_text(vjust=-1.5)) 
            
Plot_final1
```

#### Total SOC sequestration in three scenarios 

```{r Plot_f, echo=FALSE}
Plot_final2 <- ggplot(data = Df, mapping = aes(x = Year, y = SOC,
                                               group = Scenario, colour = Scenario)) +
  geom_line(size=1) +
  geom_point(size=3) +
  #scale_shape_discrete("Scenarios") +
  scale_colour_discrete("Scenarios") +
  scale_linetype_discrete("Scenarios")+
  #scale_fill_manual("SOC Incetive $/Mg CO2") +
  xlab("Time steps") + ylab(" SOC ('000 Mg CO2e) ") +
  scale_y_continuous(limits = c(0, 800), breaks = seq(0, 800, by = 160)) +
  scale_x_continuous(breaks=c(2017, 2020, 2023, 2026, 2029, 2032, 2035, 2038, 2041, 2044, 2047, 2050)) +
  theme_bw() +
  theme_classic()+
  labs(subtitle =  "Total SOC sequestration in three scenarios") +
  # theme(axis.text.x = element_text(colour = "grey20", size = 14, angle = 90, hjust = 0.5, vjust = 0.5),
  #       axis.text.y = element_text(colour = "grey20", size = 14),
  #       strip.text = element_text(face = "italic"),
  #       text = element_text(size = 16),
  #       plot.subtitle=element_text(size=20)) +
  theme(legend.position="bottom", 
        axis.title.x = element_text(vjust=-1.5)) 
Plot_final2
Legend = gtable_filter(ggplot_gtable(ggplot_build(Plot_final2)), "guide-box")

```
#### Merging the plots

```{r merge, echo=FALSE, fig.width=10, fig.height=6}

grid.arrange(grobs = list(Plot_final1+ theme(legend.position="none"), Plot_final2 + theme(legend.position="none")),
            bottom = Legend,
             height =c(10,1),
             nrow =1)   
# grid.arrange(arrangeGrob(Plot_a, Plot_b, Plot_c, top="BaU Farming", ncol=1), 
#               arrangeGrob(Plot_d, Plot_e, Plot_f + theme(legend.position="none"), top="No-Till Farming", ncol = 1), 
#              bottom = Legend,
#               ncol=2)

```

## Figure 9

#### Scenario 1
```{r merge, echo=FALSE}

std1 <- Df %>% filter(Scenario == "S1")

PlotStd1 <- 
  ggplot(std1, aes(Year, Land)) +                                     
  geom_line(color = "red", size = 1) +
  geom_point() +
  geom_errorbar(aes(ymin=Land-SD, ymax=Land+SD), width=1,
                position=position_dodge(1)) +
  xlab("Time Steps") + ylab("Land ('000 Acre)") +
  scale_y_continuous(limits = c(0, 2000), breaks = seq(0, 2000, by = 400)) +
  scale_x_continuous(breaks=c(2020, 2023, 2026, 2029, 2032, 2035, 2038, 2041, 2044, 2047, 2050)) +
  theme_bw() +
  theme_classic()+
  #labs(title = "(a) Low initial willingness scenario",
  labs(subtitle = "            S1: Price $5.5, SOC Incentive $100") +
  theme(legend.position="bottom")
PlotStd1
```

#### Scenario 2

```{r merge, echo=FALSE}
std2 <- Df %>% filter(Scenario == "S2")

PlotStd2 <- 
  ggplot(std2, aes(Year, Land)) +                                     
  geom_line(color = "red", size = 1) +
  geom_point() +
  geom_errorbar(aes(ymin=Land-SD, ymax=Land+SD), width=1,
                position=position_dodge(1)) +
  xlab("Time Steps") + ylab("Land ('000 Acre)") +
  scale_y_continuous(limits = c(0, 2000), breaks = seq(0, 2000, by = 400)) +
  scale_x_continuous(breaks=c(2020, 2023, 2026, 2029, 2032, 2035, 2038, 2041, 2044, 2047, 2050)) +
  theme_bw() +
  theme_classic()+
  #labs(title = "(a) Low initial willingness scenario",
  labs(subtitle = "            S2: Price $6, SOC Incentive $0") +
  theme(legend.position="bottom")
PlotStd2
```

#### Scenario 3

```{r merge, echo=FALSE}

std3 <- Df %>% filter(Scenario == "S3")

PlotStd3 <- 
  ggplot(std3, aes(Year, Land)) +                                     
  geom_line(color = "red", size = 1) +
  geom_point() +
  geom_errorbar(aes(ymin=Land-SD, ymax=Land+SD), width=1,
                position=position_dodge(1)) +
  xlab("Time Steps") + ylab("Land ('000 Acre)") +
  scale_y_continuous(limits = c(0, 2000), breaks = seq(0, 2000, by = 400)) +
  scale_x_continuous(breaks=c(2020, 2023, 2026, 2029, 2032, 2035, 2038, 2041, 2044, 2047, 2050)) +
  theme_bw() +
  theme_classic()+
  #labs(title = "(a) Low initial willingness scenario",
 labs(subtitle = "            S3: Price $5.5, SOC Incentive $100") +
  theme(legend.position="bottom")
PlotStd3

```

```{r merge, echo=FALSE, fig.width= 10, fig.height= 8}

grid.arrange(grobs = list(PlotStd1, PlotStd2, PlotStd3),
             height =c(10,1),
             nrow =2)
```




